Cosmic web alignments with the shape, angular momentum and peculiar velocities of dark matter halos

### 2014-02-11 paper/main.tex
working on the conclusions

The different behaviour for the alignments of massive halos in the
Tweb and the Vweb was tracked to a corresponding anti-alignment
between the eigenvectors in the two webs.

>>>>

The different behaviour for the alignments of massive halos in the
Tweb and the Vweb was tracked to a corresponding anti-alignment
between the eigenvectors in the two web grids for massive halos
$>10^{12}$\hMsun. For low mass halos the directions defined by the two
webs point in the same direction. This trends can be interpreted as
non-linear effects that appear in the two different physical
descriptions for the cosmic web.
